---
output: 
  pdf_document:
    keep_tex: true
    fig_caption: yes
    latex_engine: pdflatex
    template: ./svm-latex-syllabus.tex
geometry: margin=1in

title: "SOC 800: Comprehensive Exam Reading Prep"
author: Neal Marquez
date: "Winter 2020"

email: "nmarquez@u.washington.edu"
fontfamily: mathpazo
fontsize: 11pt
header-includes:
   - \linespread{1.05}
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='pdf')
mon <- as.Date("2018-08-27")
# fri <- as.Date("2016-01-08")
advdate <- function(obj, adv) {
 tmon <- obj + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)
 tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri)
 return(tmp)
}
library(RefManageR)
# library(knitcitations)
# library(rcrossref)
bibHisp <- ReadBib("~/Documents/bibtec/Hispanic Migration.bib",check=F)
bibDem <- ReadBib("~/Documents/bibtec/Demography.bib",check=F)
bibMig <- ReadBib("~/Documents/bibtec/Migration.bib",check=F)
myopts <- BibOptions(bib.style = "authoryear", style="latex", first.inits=FALSE, max.names = 5, no.print.fields = c("doi", "url", "isbn", "issn"))
```

## Reading List Description and Objectives

# Demography

## Overview and Evolution  

```{r, echo = FALSE, results="asis"} 
bibList <- list()

(bibList[["General"]] <- bibDem[c(
  "Coale1975", "Caldwell1996", "Greenhalgh1996", "Preston1993", "Lee2003",
  "Moffitt2005", "Xie2000", "Tienda2002", "GregJ.Duncan2008", "CALDWELL1990", 
  "Preston1996", "Bongaarts1978", "Hirschman1994"
)])
```

<!-- ## Mortaility -->
<!-- ```{r, echo = FALSE, results="asis"}  -->
<!-- bibDem[c( -->
<!--   "CALDWELL1990", "Preston1996", "McKeown1972", "Colgrove2002", "Szreter2002", -->
<!--   "Olshansky1986", "Caldwell1986", "Kuhn2010", "Link2002", "Omran2005", -->
<!--   "Clark2013", "Markides2005" -->
<!-- )] -->
<!-- ```  -->

<!-- ## Child Mortaility -->
<!-- ```{r, echo = FALSE, results="asis"}  -->
<!-- bibDem[c( -->
<!--   "Finch2003", "Geronimus1992", "Gortmaker1997", "Hamilton2009", "Hummer2007", -->
<!--   "Landale2000", "Palloni1999" -->
<!-- )] -->
<!-- ``` -->


<!-- ## Fertility -->
<!-- ```{r, echo = FALSE, results="asis"}  -->
<!-- bibDem[c( -->
<!--   "Bongaarts1978", "Hirschman1994", "Easterlin1975", "Bryant2007", -->
<!--   "Bongaarts2013", "Myrskyla2009" -->
<!-- )] -->
<!-- ``` -->

## Social Determinants and Inequality
```{r, echo = FALSE, results="asis"} 
(bibList[["social_determinants"]] <- bibDem[c(
  "Preston1975", "Preston1998", "Sampson2008", "Hayward2004", "Rogers2010", 
  "Read2006", "Singh-Manoux2005", "SZRETER1988", "Link1995", "Chetty2018",
  "Chetty2016"
)])
```

## Methods and Data
```{r, echo = FALSE, results="asis"} 
(bibList[["methods"]] <- bibDem[c(
  "Wachter", "Palmore1994", "Maine", "Preston2000", "Bhrolchain2007",
  "JC1985", "Snipp2003", "Wang2012", "Wakefield2018", "Wheldon2016", 
  "Hobcraft1982", "Raftery2014a"
)])
```

# General Migration  

## Theories of Migration  
```{r, echo = FALSE, results="asis"} 
(bibList[["migtheory"]] <- c(bibMig[c(
  "Wimmer", "Hatton2002", "Brettell2007", "Massey1993", "King2012", "Cooke2018",
  "Calnan2017", "Cadena2013", "Ellis2014", "Wang2016a"
)], bibDem[c("Morris2017", "Abel2019")]))
```

<!-- ## Division of Labor   -->
<!-- ```{r, echo = FALSE, results="asis"}  -->
<!-- (bibList[["miglabor"]] <- c(bibMig[c( -->
<!--   "Waldinger2003", "Liu2011", "Gleave2017", "Waldinger1999", "Ellis2009", -->
<!--   "SusanEckstein2018", "Kerr2016", "Smith2006", "Bound2017", "Rodriguez2010", -->
<!--   "Hanson2017", "Bean2012", "Sassen1988" -->
<!-- )])) -->
<!-- ``` -->

## Assimilation and Incorporation  
```{r, echo = FALSE, results="asis"} 
(bibList[["assim"]] <- c(bibMig[c(
  "Jimenez2017", "Massey2010a", "Portes1993", "Rumbaut1997", "Gordon1964",
  "Gans1997", "Brubaker2001", "Alba1997", "Waters2016", "Waldinger2016",
  "Waldinger2004"
)]))
```

<!-- ## Second Generation   -->
<!-- ```{r, echo = FALSE, results="asis"}  -->
<!-- (bibList[["gen2"]] <- c(bibMig[c( -->
<!--   "Luthra", "Portes", "Haller2011", "Haller2011a", "Bean2015", "Alba2011", -->
<!--   "Yoshikawa2011") -->
<!-- ])) -->
<!-- ``` -->

## Internal Migration  
```{r, echo = FALSE, results="asis"} 
(bibList[["internal"]] <- c(bibMig[c(
  "Ellis2012", "Skeldon2012", "King2010", "Molloy2011a", "Kritz2010",
  "Frey2011", "Cohen2016")], bibDem["Cooke2013"]))
```

## Context  
```{r, echo = FALSE, results="asis"} 
(bibList[["context"]] <- c(bibMig[c(
  "Clevenger2014", "Jaworsky2012", "Luthra2018", "Rumbaut2008", "Menjivar1997",
  "Flores2009", "Ellis2009a")
]))
```

# Hispanic Migration in the United States

## Historical Demographic
```{r, echo = FALSE, results="asis"} 
(bibList[["hispdemog"]] <- c(bibHisp[c(
  "Corwin", "Corwin1973", "Gonzalez-Barrera2013", "Lichter2012a", "Hall2016a",
  "Kandel2004", "Flores2017a", "Caban2003"
  )
]))
```

## Policy Changes, Immigration, and Undocumented Status  
```{r, echo = FALSE, results="asis"} 
(bibList[["policy"]] <- c(bibHisp[c(
  "Kerwin2010", "Durand2010", "Castles", "Golash-Boza2009", "Hainmueller2017",
  "VanHook2015", "Gonzales2011", "Menjivar2006", "Hall2010", "Massey2002", 
  "Hall2019b"
  ), bibMig[c("Ellis2016")]
]))
```

## Accumuolation and Networks
```{r, echo = FALSE, results="asis"} 
(bibList[["accum"]] <- c(bibHisp[c(
  "Riosmena2013", "Garip2016", "Lee2017", "Durand1986", "Levitt2006",
  "Anguiano-Tellez2007", "Alarcon2016", "Crowley2010", "Massey1986"
  )
]))
```

## New Destinations  
```{r, echo = FALSE, results="asis"} 
(bibList[["newdest"]] <- c(
  bibHisp[c(
    "Foster2018", "Durand2000", "Singer2004", "Massey2010", "Barcus2007",
    "Hall2017", "Light2009", "Singer2015", "Durand1999", "Crowley2006")],
  bibMig[c(
    "Massey2008", "Kandel2005", "Lichter2009", "Hernandez-Leon2000", "Parrado2016"
  )]
))
```